%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Front-End Engineer{\enskip\cdotp\enskip}TELUS Set-Top-Box} % Job title
    {ARX.NET} % Organization
    {Thessaloniki, Greece} % Location
    {Jan. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop front-end features for the TELUS Set-Top-Box (STB) web application in collaboration with a distributed team in the UK.}
        \item {Build reusable React and TypeScript components with Redux and TanStack Query for predictable state and data flows.}
        \item {Improve UI quality and delivery confidence through Storybook, Chromatic, Jest, and Vitest-based component and unit testing.}
        \item {Integrate REST APIs and coordinate implementation details with back-end engineers across distributed teams.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Front-End Engineer{\enskip\cdotp\enskip}Enterprise CRM} % Job title
    {ARX.NET} % Organization
    {Thessaloniki, Greece} % Location
    {Sep. 2021 - Jan. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Delivered responsive Angular and TypeScript features for an enterprise CRM platform.}
        \item {Maintained and extended core CRM modules, resolving production issues and preserving cross-browser compatibility.}
        \item {Contributed through code reviews and agile delivery practices that improved release quality.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
